Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-04-13 Paper.tex
Correct self-destruct refund semantics
The current Yellow Paper specification for the self-destruct refunds can
lead to double refunds and is not consistent with the logic clients use
to fulfill refunds in practice.

The crux of the issue is that the current Yellow Paper performs the
self-destruct refund within the SELFDESTRUCT operation of a specific EVM
invocation and each EVM invocation creates its own transaction substate
(rather than having it passed in from its parent). Therefore, although
the transaction substate is checked to see if the account has already
been included in its self-des

After the message call or contract creation is processed, the state is finalised by determining the amount to be refunded, $g^*$ from the remaining gas, $g'$, plus some allowance from the refund counter, to the sender at the original rate\footnote{Note that the total refundable gas equation prevents the gas refund from exceeding the transaction gas limit $T_{\mathrm{g}}$.}.
\begin{equation}
g^* \equiv g' + \min \left\{ \Big\lfloor \dfrac{T_{\mathrm{g}} - g'}{2} \Big\rfloor, \hyperlink{refund_balance_defn_words_A__r}{A_{\mathrm{r}}} \right\}
\end{equation}

@@

&&&& where $r = \boldsymbol{\mu}_{\mathbf{s}}[0] \bmod 2^{160}$\\

@@

&&&& $A'_{r} \equiv A_{r} + \begin{cases}
R_{selfdestruct} & \text{if} \quad I_{\mathrm{a}} \notin A_{\mathbf{s}} \\

>>>>

After the message call or contract creation is processed, the refund counter has to be incremented for the account that were self-destructed throughout its invocation.
\begin{equation}
	A'_{r} \equiv A_{r} + \sum_{i \in A_{s}} R_{selfdestruct}
\end{equation}

Then the state is finalised by determining the amount to be refunded, $g^*$ from the remaining gas, $g'$, plus some allowance from the refund counter, to the sender at the original rate.
\begin{equation}
g^* \equiv g' + \min \left\{ \Big\lfloor \dfrac{T_{\mathrm{g}} - g'}{2} \Big\rfloor, \hyperlink{refund_balance_defn_words_A__r}{A'_{\mathrm{r}}} \right\}
\end{equation}

@@

\end{cases}$\\ \\
&&&& where $r = \boldsymbol{\mu}_{\mathbf{s}}[0] \bmod 2^{160}$\\ \\

@@
